Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-01-30 msc-publication.tex
don't discuss energy measures for resting atmosphere

\begin{itemize}
	\item Comparing results BTF, SLEVE and cut cell style grid for three standard two-dimensional test cases
	\item TF grids often shown to have lesser accuracy than cut cells in some test cases, often significantly so.  Our results demonstrate that accuracy need not be much reduced and can even be better than cut cells.
	\item Small cell problem common in cut cell grids (\TODO{citations})
\end{itemize}

\section{Results}
\begin{itemize}
	\item \TODO{How much do I need to say about the model?  Just cite \citet{weller-shahrokhi2014}?}
	\item \TODO{Include BTF equations from \textcite{galchen-somerville1975} and SLEVE equations from \citet{schaer2002}?}
	\item \TODO{Explain how SnapCol grid is constructed?}
\end{itemize}

@@

@@

	schaer-4thorder \\
	\includegraphics[height=1.5in]{schaer-btf-4thorder.png}
	\includegraphics[height=1.5in]{schaer-btf-4thorder-error.png}
%
	\caption{Comparing our BTF cubicUpwindCPCFit result with Schaer's 4th order result}
	\label{fig:advection}
\end{figure}

@@

\TODO{do we want to discuss energy measures?  1. we can't compare our results with anybody else, 2. we'll have to explain how we calculate the energy measures 3. it could open a can of worms w.r.t. lack of conservation}

@@

Analysis:
\begin{itemize}
	\item Spurious $w$ significantly less than those found by \citet{klemp2011} for BTF: \SI{0.35}{\meter\per\second} vs \SI{10}{\meter\per\second}
	\item SnapCol $w$ (\SI{1e-3}{\meter\per\second}) significantly lower and energy conservation better than BTF or SLEVE
	\item Formulation is not energy conserving
	\item \TODO{Could also compare with \textcite{zaengl2012}, \citet{good2014}?}
	\item Conclusion: non-orthogonality is a significant cause of numerical error in this test but, again, satisfactory on all grids
\end{itemize}

@@

Miscellany:
\begin{itemize}
	\item Advection accuracy depends on alignment of the flow with grid layers (\TODO{we kinda need wobblyTracerAdvection to reach this conclusion})
	\item Formulation does not conserve energy (evidenced in resting atmosphere test, Fig 4.12d in MSc dissertation)
\end{itemize}

>>>>

\begin{itemize}
	\item A sentence or two about why orography is important to represent in NWP
	\item Comparing results BTF, SLEVE and cut cell style grid for three standard two-dimensional test cases
	\item TF grids often shown to have lesser accuracy than cut cells in some test cases, often significantly so.  Our results demonstrate that accuracy need not be much reduced and can even be better than cut cells.
	\item Small cell problem common in cut cell grids (\TODO{citations})
\end{itemize}

\section{Results}
\begin{itemize}
	\item \TODO{How much do I need to say about the model?  -- Give a summary: what equation set? finite volume with curl-free pressure grad; lorenz grid; advection scheme}
	\item \TODO{Include BTF equations from \textcite{galchen-somerville1975} and SLEVE equations from \citet{schaer2002}?}
	\item \TODO{Explain how SnapCol grid is constructed?}
\end{itemize}

@@

\TODO{should we just compare cubicUpwindCPCFit with Sch\"ar's 4th order?  We could also compare our skewCorrected linear with Sch\"ar's linear but I'm not sure what value it would have...}

@@

	schaer-4thorder \\
	\includegraphics[height=1.5in]{schaer-btf-4thorder.png}
	\includegraphics[height=1.5in]{schaer-btf-4thorder-error.png}

	\TODO{also include SnapCol results}
	\TODO{check error contours are correct (0.01?)}
%
	\caption{Comparing our BTF cubicUpwindCPCFit result with Schaer's 4th order result}
	\label{fig:advection}
\end{figure}

@@

@@

Analysis:
\begin{itemize}
	\item Spurious $w$ significantly less than those found by \citet{klemp2011} for BTF: \SI{0.35}{\meter\per\second} vs \SI{10}{\meter\per\second}
	\item SnapCol $w$ (\SI{1e-3}{\meter\per\second}) significantly than BTF or SLEVE
	\item \TODO{Could also compare with \textcite{zaengl2012}, \citet{good2014}?}
	\item Conclusion: non-orthogonality is a significant cause of numerical error in this test but, again, satisfactory on all grids
\end{itemize}

@@

Miscellany:
\begin{itemize}
	\item Advection accuracy depends on alignment of the flow with grid layers (\TODO{we kinda need wobblyTracerAdvection to reach this conclusion})
\end{itemize}
